---
title: "renderCountySummaries"
author: "dan carver"
date: "11/13/2020"
output: html_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(raster)
library(dplyr)
library(sf)
library(tmap)
library(plotly)
library(psych)
library(DT)
tmap_mode("view")

nlcdPallette <- c("#486da2", "#f10100", "#b3afa4", "#1d6533",
                  "#b0963f", "#d0d181", "#ae722a", "#bbd7ed")
nlcdClasses <- c("water", "developed", "barren", "forest",
                 "scrub", "grassland", "crops", "wetlands")
```

This script will be called to generate some statistical summaries and area visualizations for the various counties of interest

Map showing the land cover data for the county. [data source](https://www.mrlc.gov/data/nlcd-2016-land-cover-conus)
```{r echo=FALSE, message=FALSE, warning=FALSE}
vals <- unique(values(lc2))
vals <- sort(vals[!is.na(vals)])
nlcdPallette <- nlcdPallette[vals]
nlcdClasses <- nlcdClasses[vals]
m1 <- tm_shape(lc2) +
    tm_raster(style = "cat", palette = nlcdPallette, labels = nlcdClasses, title = "Land Cover")+
  tm_layout(legend.outside = TRUE)
m1
```
<br><br>
***
<br>

Map showing the estimated population across the county. Open areas are zero. [data source](https://ghsl.jrc.ec.europa.eu/ghs_pop2019.php)
```{r echo=FALSE, message=FALSE, warning=FALSE}
pop2[pop2[] == 0] <- NA
pop2[pop2[] == -0] <- NA

m2 <- tm_shape(pop2) +
    tm_raster(style = "kmeans", n = 5, palette = "YlGnBu", title = "Population")
m2
```
<br>
<br>

# Various Distributions {.tabset .tabset-fade .tabset-pills}

```{r echo=FALSE, message=FALSE, warning=FALSE}
# call function to generate plots
p1 <- values(rad)
p1 <- p1[!is.na(p1)]
b1 <- c(0, 1, 2, 3, 5, 8, 13, 21, 34, 55, 89, 144, 233, 377, 610)
b1 <- append(b1[b1 < max(p1)], max(p1))
```

## All values
```{r echo=FALSE, message=FALSE, warning=FALSE}
#
p2 <- p1

fig <- plot_ly(x = p2,
             type = "histogram") %>%
layout(title = 'All Radience Values',
         xaxis = list(title = 'Radience in nanowatts',
                      zeroline = TRUE),
         yaxis = list(title = 'Count of Pixels'))

fig
```
Histogram shows number of pixels within each bin 

```{r echo=FALSE, message=FALSE, warning=FALSE}
d2 <-psych::describe(p2, IQR = TRUE)
DT::datatable(d2)
```
<br><br>
Summary statistics of the pixel values 
<br><br> 
```{r echo=FALSE, message=FALSE, warning=FALSE}
# reset for min vals
b1 <- sort(unique(append(b1[b1 >= min(p2)], min(p2))))
tm_shape(rad) +
  tm_raster(style = "fixed", breaks =b1, title = "radiance")

```
Map showing the distribution of the radiance values 

## Values Greatern then 1
```{r echo=FALSE, message=FALSE, warning=FALSE}
#
p2 <- p1[p1 >= 1]

fig <- plot_ly(x = p2,
             type = "histogram") %>%
layout(title = 'All Radience Values',
         xaxis = list(title = 'Radience in nanowatts',
                      zeroline = TRUE),
         yaxis = list(title = 'Count of Pixels'))

fig
```
Histogram shows probabilities of feature within  
```{r echo=FALSE, message=FALSE, warning=FALSE}
d2 <-psych::describe(p2, IQR = TRUE)
DT::datatable(d2)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
# reset for min vals
b1 <- sort(unique(append(b1[b1 >= min(p2)], min(p2))))
rad1 <- rad
rad1[rad1[] < min(p2)] <- NA
tm_shape(rad1) +
  tm_raster(style = "fixed", breaks =b1, title = "radiance")

```

## Values Greatern then 2
```{r echo=FALSE, message=FALSE, warning=FALSE}
#
p2 <- p1[p1 >= 2]

fig <- plot_ly(x = p2,
             type = "histogram") %>%
layout(title = 'All Radience Values',
         xaxis = list(title = 'Radience in nanowatts',
                      zeroline = TRUE),
         yaxis = list(title = 'Count of Pixels'))

fig
```
Histogram shows probabilities of feature within  
```{r echo=FALSE, message=FALSE, warning=FALSE}
d2 <-psych::describe(p2, IQR = TRUE)
DT::datatable(d2)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
# reset for min vals
b1 <- sort(unique(append(b1[b1 >= min(p2)], min(p2))))
rad1 <- rad
rad1[rad1[] < min(p2)]<- NA
tm_shape(rad1) +
  tm_raster(style = "fixed", breaks =b1, title = "radiance")

```

## Values Greatern then 3
```{r echo=FALSE, message=FALSE, warning=FALSE}
#
p2 <- p1[p1 >= 3]

fig <- plot_ly(x = p2,
             type = "histogram") %>%
layout(title = 'All Radience Values',
         xaxis = list(title = 'Radience in nanowatts',
                      zeroline = TRUE),
         yaxis = list(title = 'Count of Pixels'))

fig
```
Histogram shows probabilities of feature within  
```{r echo=FALSE, message=FALSE, warning=FALSE}
d2 <-psych::describe(p2, IQR = TRUE)
DT::datatable(d2)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
# reset for min vals
b1 <- sort(unique(append(b1[b1 >= min(p2)], min(p2))))
rad1 <- rad
rad1[rad1[] < min(p2)]<- NA
tm_shape(rad1) +
  tm_raster(style = "fixed", breaks =b1, title = "radiance")

```

## Values Greatern then 4
```{r echo=FALSE, message=FALSE, warning=FALSE}
#
p2 <- p1[p1 >= 4]

fig <- plot_ly(x = p2,
             type = "histogram") %>%
layout(title = 'All Radience Values',
         xaxis = list(title = 'Radience in nanowatts',
                      zeroline = TRUE),
         yaxis = list(title = 'Count of Pixels'))

fig
```
Histogram shows probabilities of feature within  
```{r echo=FALSE, message=FALSE, warning=FALSE}
d2 <-psych::describe(p2, IQR = TRUE)
DT::datatable(d2)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# reset for min vals
b1 <- sort(unique(append(b1[b1 >= min(p2)], min(p2))))
rad1 <- rad
rad1[rad1[] < min(p2)]<- NA
tm_shape(rad1) +
  tm_raster(style = "fixed", breaks =b1, title = "radiance")

```

## Values Greatern then 5
```{r echo=FALSE, message=FALSE, warning=FALSE}
#
p2 <- p1[p1 >= 5]

fig <- plot_ly(x = p2,
             type = "histogram") %>%
layout(title = 'All Radience Values',
         xaxis = list(title = 'Radience in nanowatts',
                      zeroline = TRUE),
         yaxis = list(title = 'Count of Pixels'))

fig
```
Histogram shows probabilities of feature within  
```{r echo=FALSE, message=FALSE, warning=FALSE}
d2 <-psych::describe(p2, IQR = TRUE)
DT::datatable(d2)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
# reset for min vals
b1 <-sort(unique(append(b1[b1 >= min(p2)], min(p2))))
rad1 <- rad
rad1[rad1[] < min(p2)]<- NA
tm_shape(rad1) +
  tm_raster(style = "fixed", breaks =b1, title = "radiance")

```

## Values Greatern then 6
```{r echo=FALSE, message=FALSE, warning=FALSE}
#
p2 <- p1[p1 >= 6]

fig <- plot_ly(x = p2,
             type = "histogram") %>%
layout(title = 'All Radience Values',
         xaxis = list(title = 'Radience in nanowatts',
                      zeroline = TRUE),
         yaxis = list(title = 'Count of Pixels'))

fig
```
Histogram shows probabilities of feature within  
```{r echo=FALSE, message=FALSE, warning=FALSE}
d2 <-psych::describe(p2, IQR = TRUE)
DT::datatable(d2)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
# reset for min vals
b1 <- sort(unique(append(b1[b1 >= min(p2)], min(p2))))
rad1 <- rad
rad1[rad1[] < min(p2)]<- NA
tm_shape(rad1) +
  tm_raster(style = "fixed", breaks =b1, title = "radiance")

```


Maps of each threshold value
