---
title: "downTownAZ"
author: "dan carver"
date: "3/5/2021"
htmlwidgets: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(plotly)
library(raster)
library(tmap)
```


# tucson 

## Down Town Area 


```{r}
feb <- raster::raster("F:/geoSpatialCentroid/covidNightLights/data/correct2020imagery/feburary/Pima.tif")
mar <- raster::raster("F:/geoSpatialCentroid/covidNightLights/data/correct2020imagery/march/Pima.tif")
downtown <- raster::shapefile("F:/geoSpatialCentroid/covidNightLights/data/Tucson/downtownArea/downTownTucson.shp")

febC <- raster::crop(x = feb, y = downtown[1,])%>%raster::mask(mask = downtown[1,])
marC <- raster::crop(x = mar, y = downtown[1,])%>%
  raster::mask(mask = downtown[1,])

#county level 
fcv <- raster::values(feb)
fcv[fcv < 2 ] <- NA
fcv <- fcv[!is.na(fcv)]

mcv <- raster::values(mar)
mcv[mcv < 2 ] <- NA
mcv <- mcv[!is.na(mcv)]

# town level 
fdv <- raster::values(febC)
fdv <- fdv[!is.na(fdv)]

mdv <- raster::values(marC)
mdv <- mdv[!is.na(mdv)]

# histogram
fig <- plot_ly(
  type='histogram',
  x= fdv,
  alpha = 0.6,
  bingroup=1,
  name = 'Feb Values')

fig <- fig %>% add_trace(
  type='histogram',
  x=mdv,
  alpha = 0.6,
  bingroup=1,
  name = "Mar Values")

fig <- fig %>% layout(
  barmode="group",
  bargap=0.1)

fig
htmlwidgets::saveWidget(as_widget(fig), "index.html")
```


<br>
<br>
<br>
Down town area. 11 pixels. March and February presented
<br>
<br>
<br>

```{r}
tmap_mode("view")
m1 <- tm_shape(febC )+
  tm_raster(title = "feb", breaks = c(seq(30,100, by = 10)))+
  tm_shape(downtown[1,])+
  tm_borders(col = "grey")
m2 <- tm_shape(marC )+
  tm_raster(title = "mar", breaks = c(seq(30,100, by = 10)))+
  tm_shape(downtown[1,])+
  tm_borders(col = "grey")

tmap_arrange(m1, m2, sync = TRUE)


```

<br>
<br>
<br>
<br>
<br>

### County level summary

<br>
<br>
<br>
<br>

```{r}
# histogram
fig <- plot_ly(
  type='histogram',
  x= fcv,
  alpha = 0.6,
  bingroup=1,
  name = 'Feb Values')

fig <- fig %>% add_trace(
  type='histogram',
  x=mcv,
  alpha = 0.6,
  bingroup=1,
  name = "Mar Values")

fig <- fig %>% layout(
  barmode="group",
  bargap=0.1)

fig
```

<br>
<br>

Histograms of the full county. I drop all values less the 2 as they accounted for ~90 of all observations within the corrected datasets. There does seems to be more low end values in march then in Feb, but I would want to make the comparison without limiting the low values before making assumptions about this observation.

<br>
<br>

```{r}
tmap_mode("view")
m1 <- tm_shape(feb )+
  tm_raster(title = "feb", breaks = c(seq(0,200, by = 20)), colorNA = NULL)+
  tm_shape(downtown[1,])+
  tm_borders(col = "grey")
m2 <- tm_shape(mar )+
  tm_raster(title = "mar", breaks = c(seq(0,200, by = 20)), colorNA = NULL)+
  tm_shape(downtown[1,])+
  tm_borders(col = "grey")
tmap_arrange(m1, m2, sync = TRUE)

```



<br>
<br>
<br>

