---
title: "yearlyCountySummaries"
author: "dan carver"
date: "11/13/2020"
output: html_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
nlcdPallette <- c("#486da2", "#f10100", "#b3afa4", "#1d6533",
                  "#b0963f", "#d0d181", "#ae722a", "#bbd7ed")
nlcdClasses <- c("water", "developed", "barren", "forest",
                 "scrub", "grassland", "crops", "wetlands")
b1 <- c(0, 1, 2, 3, 5, 8, 13, 21, 34, 55, 89, 144, 233, 377, 610)

```

This script will be called to generate some statistical summaries and area visualizations for the various counties of interest

Map showing the land cover data for the county. [data source](https://www.mrlc.gov/data/nlcd-2016-land-cover-conus)
```{r echo=FALSE, message=FALSE, warning=FALSE}
vals <- unique(values(lc2))
vals <- sort(vals[!is.na(vals)])
nlcdPallette <- nlcdPallette[vals]
nlcdClasses <- nlcdClasses[vals]
m1 <- tm_shape(lc2) +
    tm_raster(style = "cat", palette = nlcdPallette, labels = nlcdClasses, title = "Land Cover")+
  tm_layout(legend.outside = TRUE)
m1
```
<br><br>
***
```{r echo=FALSE, message=FALSE, warning=FALSE}
urban <- lc2 
urban[urban[] != 2,] <- NA
crops <- lc2
crops[crops[] != 8,] <- NA
forest <- lc2
forest[forest[] != 4,] <- NA
```


# Summary of yearly median based on land cover {.tabset .tabset-fade .tabset-pills}

## Urban 
```{r echo=FALSE, message=FALSE, warning=FALSE}
urban[urban[]==2, ]<- 1
uM <- urban * me1
p1 <- values(uM)
p1 <- p1[!is.na(p1)]

b2 <- append(b1[b1 < max(p1)], max(p1))

tm_shape(uM) +
  tm_raster(style = "fixed", breaks =b2, title = "radiance")
```

Map showing the median yearly radiance for 2016 for all land cover classified as urban. Not that roads are considered urban areas. 
<br>
<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}

d2 <-psych::describe(p1, IQR = TRUE)
DT::datatable(d2)
```
Table describing the summary statistics for all urban areas in 2016


<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}
#
p2 <- p1

fig <- plot_ly(x = p2,
             type = "histogram") %>%
layout(title = 'All Radience Values',
         xaxis = list(title = 'Radience in nanowatts',
                      zeroline = TRUE),
         yaxis = list(title = 'Count of Pixels'))

fig
```
Distribution of values in the urban area for 2016



## Forest 
```{r echo=FALSE, message=FALSE, warning=FALSE}
forest[forest[]==4, ]<- 1
uM <- forest * me1
p1 <- values(uM)
p1 <- p1[!is.na(p1)]

b2 <- append(b1[b1 < max(p1)], max(p1))

tm_shape(uM) +
  tm_raster(style = "fixed", breaks =b2, title = "radiance")
```

Map showing the median yearly radiance for 2016 for all land cover classified as forested.
<br>
<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}

d2 <-psych::describe(p1, IQR = TRUE)
DT::datatable(d2)
```
Table describing the summary statistics for all forested areas in 2016


<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}
#
p2 <- p1

fig <- plot_ly(x = p2,
             type = "histogram") %>%
layout(title = 'All Radience Values',
         xaxis = list(title = 'Radience in nanowatts',
                      zeroline = TRUE),
         yaxis = list(title = 'Count of Pixels'))

fig
```
Distribution of values in the forsted area for 2016



## Crops 
```{r echo=FALSE, message=FALSE, warning=FALSE}
crops[crops[]==8, ]<- 1
uM <- forest * me1
p1 <- values(uM)
p1 <- p1[!is.na(p1)]

b2 <- append(b1[b1 < max(p1)], max(p1))

tm_shape(uM) +
  tm_raster(style = "fixed", breaks =b2, title = "radiance")
```

Map showing the median yearly radiance for 2016 for all land cover classified as crops
<br>
<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}

d2 <-psych::describe(p1, IQR = TRUE)
DT::datatable(d2)
```
Table describing the summary statistics for all crop areas in 2016


<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}
#
p2 <- p1

fig <- plot_ly(x = p2,
             type = "histogram") %>%
layout(title = 'All Radience Values',
         xaxis = list(title = 'Radience in nanowatts',
                      zeroline = TRUE),
         yaxis = list(title = 'Count of Pixels'))

fig
```
Distribution of values in the crop area for 2016




