---
title: "monthlyComparisions of Night Lights Data"
author: "dan carver"
date: "10/1/2020"
output: html_document
---

For Santa Rosa and Dhaka show the changes in night light values between Jan-Feb and Feb-Mar 2020 



```{r echo=FALSE, message=FALSE, warning=FALSE}
library(raster)
library(dplyr)
library(sf)
library(tmap)
tmap_mode("view")

# baseDir
baseDir <- "F:/nrelD/geoSpatialCentroid/covidNightLights"

crm <- function(r,template){
  # r is a raster
  # template is a raster 
  # crs need to be the same 
  r1 <- r %>%
  raster::crop(template) %>%
  raster::resample(y = template, method = "bilinear")%>%
  raster::mask(template)
  return(r1)
}

```


```{r echo=FALSE, message=FALSE, warning=FALSE}

# global settlement layers, these I huge I need to deal with them first. 
pop <- raster::raster("F:/nrelD/genericSpatialData/world/globalHumanSettlement/GHS_POP_E2015_GLOBE_R2019A_54009_250_V1_0/GHS_POP_E2015_GLOBE_R2019A_54009_250_V1_0.tif")
built <- raster::raster("F:/nrelD/genericSpatialData/world/globalHumanSettlement/GHS_BUILT_LDS2014_GLOBE_R2018A_54009_250_V2_0/GHS_BUILT_LDS2014_GLOBE_R2018A_54009_250_V2_0.tif")
mCRS <- pop@crs

### Extent layers 
extents <- sf::read_sf("F:/nrelD/geoSpatialCentroid/covidNightLights/data/fromGEE/extentLocations.shp")
sExtent <- extents[3,]%>%
  sf::st_transform(crs = mCRS)
dExtent <- extents[1,]%>%
  sf::st_transform(crs = mCRS)

# lat long 
lCRS <-  crs("+proj=longlat +datum=WGS84 +no_defs")

spop <- raster::crop(x = pop, y = sExtent) %>%
  raster::projectRaster(crs = lCRS)
dpop <- raster::crop(x = pop, y = dExtent)%>%
  raster::projectRaster(crs = lCRS)
rm(pop)

sbuilt <- raster::crop(x = built, y = sExtent)%>%
  raster::projectRaster(crs = lCRS)
dbuilt <- raster::crop(x = built, y = dExtent)%>%
  raster::projectRaster(crs = lCRS)
rm(built)





# read in layers 
## santa rosa 
sJ <-raster::raster("F:/nrelD/geoSpatialCentroid/covidNightLights/data/2020/janurary/santaRosa.tif")
sF <-raster::raster("F:/nrelD/geoSpatialCentroid/covidNightLights/data/2020/feburary/santaRosa.tif")
sM <-raster::raster("F:/nrelD/geoSpatialCentroid/covidNightLights/data/2020/march/santaRosa.tif")
# dhaka 
dJ <- raster::raster("F:/nrelD/geoSpatialCentroid/covidNightLights/data/2020/janurary/dhaka.tif")
dF <- raster::raster("F:/nrelD/geoSpatialCentroid/covidNightLights/data/2020/feburary/dhaka.tif")
dM <- raster::raster("F:/nrelD/geoSpatialCentroid/covidNightLights/data/2020/march/dhaka.tif")

```

<br>

## Dhaka Bangladesh 

The map is constructed around the general area of Dhaka Bangladesh 
All radiance values that were < 1 for each month were replace with NA values. This can be change but was down to filter out low light areas


**Note: The cell size of these images are much larger then when they are collected. These visualizations below are meant to indentify general areas of interest**

<br>
```{r echo=FALSE, message=FALSE, warning=FALSE}
### Drop all low level values
dJ[dJ[] < 1 ,] <-NA 
dF[dF[] < 1 ,] <-NA 
dM[dM[] < 1 ,] <-NA 

# jan - feb diff 
djf <- dJ - dF

# feb - mar diff
dfm <- dF - dM

### crop and resample world pop and build layers 
dpopjf <- crm(r = dpop, template = djf)
dpopfm <- crm(r = dpop, template = dfm)

dbuiltjf <- crm(r = dbuilt, template = djf)
dbuiltfm <- crm(r = dbuilt, template = dfm)


### jan feb map 
djfMap <- tm_shape(dbuiltjf, name = "build envir")+
  tm_raster(title = "% Built Environment") +
  tm_shape(dpopjf, name = "population")+
  tm_raster(title = "total population")+
  tm_shape(djf, name ="radiance")+
  tm_raster(title = "jan - feb radience", n =10)
  

### feb mar map 
dfmMap <- tm_shape(dbuiltfm, name = "build envir")+
  tm_raster(title = "% Built Environment") +
  tm_shape(dpopfm, name = "population")+
  tm_raster(title = "total population")+
  tm_shape(dfm,name = "radience")+
  tm_raster(title = "feb - mar radience", n =10)
  

```
<br>


### Change in radience between Jan and Feb 2020

<br>

- Postive values indicate the Janurary was brighter

- Negative values indicate that Feburary was brighter

<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}
djfMap

```
<br>


### Change in radience between Feb and March 2020

<br>

- Postive values indicate the Feburary was brighter

- Negative values indicate that March was brighter

<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}
dfmMap

```
<br>


## Santa Rosa, United States of America

<br>

The map is constructed around the general area of Santa Rosa,CA, USA. 
All radiance values that were < 1 for each month were replace with NA values. This can be change but was down to filter out low light areas


**Note: The cell size of these images are much larger then when they are collected. These visualizations below are meant to indentify general areas of interest**

<br>
```{r echo=FALSE, message=FALSE, warning=FALSE}
### Drop all low level values
sJ[sJ[] < 1 ,] <-NA 
sF[sF[] < 1 ,] <-NA 
sM[sM[] < 1 ,] <-NA 


# jan - feb diff 
sjf <- sJ - sF
# feb - mar diff
sfm <- sF - sM

### crop and resample world pop and build layers 
spopjf <- crm(r = spop, template = sjf)
spopfm <- crm(r = spop, template = sfm)

sbuiltjf <- crm(r = sbuilt, template = sjf)
sbuiltfm <- crm(r = sbuilt, template = sfm)


### jan feb map 
sjfMap <- tm_shape(sbuiltjf, name = "build envir")+
 tm_raster(title = "% Built Environment") +
 tm_shape(spopjf, name = "population")+
 tm_raster(title = "total population")+
 tm_shape(sjf, name = "radience")+
 tm_raster(title = "jan - feb radience", n = 10)
 
### feb mar map 
sfmMap <- tm_shape(sbuiltfm, name = "build envir")+
 tm_raster(title = "% Built Environment") +
 tm_shape(spopfm, name = "population")+
 tm_raster(title = "total population")+
 tm_shape(sfm, name = "radience")+
 tm_raster(title = "feb - mar radience" , n =10)
 
```
<br>

### Change in radience between Jan and Feb 2020

<br>

- Postive values indicate the Janurary was brighter

- Negative values indicate that Feburary was brighter


```{r echo=FALSE, message=FALSE, warning=FALSE}

sjfMap
```
<br>

### Change in radience between Feb and March 2020

<br>

- Postive values indicate the Feburary was brighter

- Negative values indicate that March was brighter


Change the base map to open street map and you can see what under the areas of high change

1. valero benicia refinery 

2. San Fransico Airport

3. alamenda county complex 

<br>

```{r echo=FALSE, message=FALSE, warning=FALSE}

sfmMap
```


